SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Add references

---
title: "SimBio: a flexible and extensible Python package for systems modelling"
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
---

@@

Several tools already exist to define and simulate these systems.
In particular,
Biosimulators.org,
a registry of simulation tools,
list at least 15 Python softwares
among which are included
COPASI,
Tellurium,
GillesPy2
PySB.
However,
some are only Python wrappers to external (C, C++) libraries.
They allow to "control" the model definition and simulation in a Python script,
but it is not possible to use existing Python packages
to change the way the simulation is carried out.
In other words, they are not extensible from Python.

@@

>>>>

---
title: "SimBio: a flexible and extensible Python package for systems modelling"
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
---

@@

Several tools already exist to define and simulate these systems.
In particular,
Biosimulators.org,
a registry of simulation tools,
list at least 15 Python softwares
among which are included
COPASI [@hoopsCOPASICOmplexPAthway2006],
Tellurium [@choiTelluriumExtensiblePythonbased2018],
GillesPy2 [@matthewGillesPy2BiochemicalModeling2023]
PySB [@lopezProgrammingBiologicalModels2013].
However,
some are only Python wrappers to external (C, C++) libraries.
They allow to "control" the model definition and simulation in a Python script,
but it is not possible to use existing Python packages
to change the way the simulation is carried out.
In other words, they are not extensible from Python.

@@

# References

::: {#refs}
:::
